The subject of this project is : 'Research and implementation of cyber attacks'. To cover this large subject, it is mandatory to set boundaries and limits to what will be done.
The main purpose of this paper will be researching and implementing minimal software and scripts for the automation of web penetration testing. Firstly, a vulnerable lab will be required in order to test out the features that will be developed later on. To do so, a slightly modified version of DVWA (Damn Vulnerable Web Application) will be used as a base to convey attacks. This setup will all be possible through an Ansible script in order to be able to build new vulnerable machines in one command. When the "defence" side will be ready to go, the attack side will be built on the same requirements. \\ Indeed, it has to be possible to build an attacker machine as easy as a defender one in order for the work to be replicated fast. The attacker machine will be able to deploy an aggressive script that will use classic automated tools to attack the defender machine. This script aim to be the most generic possible in order to aim it at another website than DVWA if needed but some part of it will be really specific to DVWA as automation is not always easy. Discretion or anonymization will not be important in this work as we attack in legal terms a machine that we own. \\ 
\textbf{DISCLAIMER :} The author of this paper is not responsible for any use outside legal conditions, this project only has research and scientifical purpose and do not aim to target actual websites. \\
The attacking script should give some outputs that could be used to further investigate the pentest by hand, but also give informations about the website and/or things that could be exploited automatically (database dumps for example). However, some things will not be covered by the script as DOS (Denial of service) or dropping tables, because information gathering is the purpose of this paper and of the attack that will be carried, not destructive behavior. \\
The last stage of the project will be to build a script that is able to detect and maybe intercept the attacks of the attacking script. This defence scipt will be minimal because most of the attacks covered in this project are basics one and the automation is easily detectable because it is spamming the vulnerable web application. In order to do so, a list of banned IP addresses will be buid and the script will block them for requesting the website for a certain amount of time in order for the spamming to be impossible and therefore the automatic pentest will be down.